\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-05-24 paper/jitp_rr_memo/jitp_rr_memo.tex
finished addressing points from R1

>>>>

	\textbf{Response}: We have added a paragraph to the conclusion in which we recap the uses of website content analysis that we reviewed in the front end of the paper, and also note and cite potential applications outside of the analysis of government websites and candidates. We give examples of politics and policy research in which researchers have analyzed (1) company websites, and (2) the websites of interest groups.

### 2021-05-24 paper/manuscript_jitp_rr.tex
finished addressing points from R1

The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents. Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and  verall function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities. The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S. Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.

@@

>>>>

The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents. Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities. The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S. Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.

@@

Above we reviewed several research projects that involved the analysis of government websites \citep{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}, and those of politicians or candidates in elections  \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. Our pipeline would be applicable to projects such as these. However, the application of the methods we propose is not limited to government and politician websites. Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites. For example, \citet{coyle2020no} analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models. \citet{kluver2015measuring} use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies. There is a broad body of research programs that could make use of the data collection and processing pipeline we present.
